Security on Networks

### 2013-05-16 paper/paper.tex

A random attacker then chooses one of the $n$ agents uniformly at random and exposes this agent to infection. If the chosen agent $i$ is not immunized, the infection spreads to all susceptible agents on the component of agent $i$. We define $\textbf{P}(A, \textbf{q})$ to be the probability of infection of an agent on random graph $A$ when the agents collectively play security profile $\textbf{q}$. The utility function of agent $i$ is given by:
\begin{eqnarray}
	u_i(q_i) = -\textbf{P}(A, \textbf{q}) - c(q_i)
\end{eqnarray} 
We define $\tilde{\textbf{P}}(A,q_{-i})$ to be the probability that agent $i$ is exposed to infection given that all other agents play security profile $q_{-i}$. Then, using a result from Acemoglu et al., we can rewrite the utility function as:
\begin{eqnarray}
	u_i(q_i) = -(1-q_{i})\tilde{\textbf{P}}(A,q_{-i}) - c(q_i)
\end{eqnarray}
Next, we define social welfare $W(\textbf{q})$ to be the sum of the utilities of all agents, namely:
\begin{eqnarray}
	W(\textbf{q}) = \sum\limits_{i \in A} u_i(q_i) = \sum\limits_{i \in A}  -(1-q_{i})\tilde{\textbf{P}}(A,q_{-i}) - c(q_i)
\end{eqnarray}
In the case of a Nash equilibrium, each agent chooses $q_i$ to maximize his utility function given that the remaining agents collectively play $q_{-i}$. In the case of the social optimum, each agent chooses $q_i$ to maximize social welfare given $q_{-i}$.

@@

\subsection{Simulation Results}

@@

>>>>

A random attacker then chooses one of the $n$ agents uniformly at random and exposes this agent to infection. If the chosen agent $i$ is not immunized, the infection spreads to all susceptible agents on the component of agent $i$. We define $\textbf{P}(A, \textbf{q})$ to be the probability of infection of agent $i$ on random graph $A$ when the agents collectively play security profile $\textbf{q}$. The utility function of agent $i$ is given by:
\begin{eqnarray}
	u_i(q_i) = -\textbf{P}(A, \textbf{q}) - c(q_i)
\end{eqnarray} 
We define $\tilde{\textbf{P}}(A,q_{-i})$ to be the probability that agent $i$ is exposed to infection given that all other agents play security profile $q_{-i}$. Then, using a result from Acemoglu et al., we can rewrite the utility function as:
\begin{eqnarray}
	u_i(q_i) = -(1-q_{i})\tilde{\textbf{P}}(A,q_{-i}) - c(q_i)
\end{eqnarray}
Next, we define social welfare $W(\textbf{q})$ to be the sum of the utilities of all agents, namely:
\begin{eqnarray}
	W(\textbf{q}) = \sum\limits_{i \in A} u_i(q_i) = \sum\limits_{i \in A}  -(1-q_{i})\tilde{\textbf{P}}(A,q_{-i}) - c(q_i)
\end{eqnarray}
In the case of a Nash equilibrium, each agent chooses $q_i$ to maximize his utility function given that the remaining agents collectively play $q_{-i}$. In the case of the social optimum, each agent chooses $q_i$ to maximize social welfare given $q_{-i}$.

@@

\subsection{Static Simulation Results}

@@

\subsection{Simulating the Dynamic Model}

We analyze agents dynamically choosing security. Similar to the SIR model introduced in class, we present the notion of attacking and curing nodes as agents choose their level of security at each timestep. We begin by using an Erd\H{o}s-R\'{e}nyi graph. However, in some applications, as with the case with the spread of infectious disease, the Barbasi-Albert preferential attachment model may be preferable for a higher clustering coefficient and may better mimic the choice of selecting a new partner. In the preferential attachment model with a parameter $k$, we start with $k$ nodes that are completely connected. For each node added to the graph, we add $k$ edges, weighted by the degrees of the current nodes in the graph.

Agents are fully informed of the attack and cure probabilities, as well as the security levels chosen by their neighbors in the previous timestep. The attack probability is equivalent to the infection rate $\alpha$ in the SIR model, i.e. the probability that a currently uninfected node will be infected at the next timestep. Similarly, the cure probability is analogous to the recovery rate $\gamma$, i.e. the probability that a currently infected node will no longer be infected at the next timestep.

At each time step, each agent chooses its level of security based on the levels of security of its neighborhood from the previous round and the attack and cure probabilities. The neighborhood of a node is defined for a pre-determined scope, indicating how deep into the graph an agent can see. For example, a scope of $1$ indicates that  agent $i$ can only view the choices of its neighbors and a scope of $2$ means that it can also see the choices of its neighbor's neighbors.

For dynamic simulations, we use a default cost function of $c(q) = q^2$. Given that the cure probability is $\gamma$ and the attack probability is $\alpha$, the probability that the infection reaches agent $i$ is:
\begin{equation}
	\tilde{\textbf{P}}(A,q_{-i}) = 1 - (1 - \gamma) \prod_{n \in N(i)}{(1-P_n)}
\end{equation}
where $P_n$ is the probability of the infection reaching its neighbor. For a scope of 1, because the agent can only see a certain scope through the graph, it assumes that if it is infected, it will be no longer infected by the next time step by the cure probability and that if it is not infected, it will be infected with a probability of the attack probability. For larger scopes, the node also uses information about its neighbor's neighbors to determine the probability that infection will reach it.

\subsection{Dynamic Simulation Results}
